\doublespacing

I would like to extend my sincerest gratitude to my research advisor, Dr. Michael R. Peterson. He went above and beyond not only to induct me into the fractional quantum Hall community, but also to inspire me as both a mentor and role model for what it means to pursue your passion in physics research. Thank you for your undying support through no matter what came our way.

I would like to thank my thesis committee members, Dr. Andreas Bill and Dr. Jiyeong Gu, for their time, advice, and friendly words in the hall.

I thank Ryan Towne for calculating benchmarks used in this thesis.

I thank Dr. Prashanth Jaikumar for his excellent instruction and advising.

I thank Dr. Zoltan Papp for his excellent instruction as well as the time, mentoring, laughs, and kindness he gave while working as his graduate assistant.

I thank Dr. Chuhee Kwon for her excellent instruction, support, and kind words.

I thank the staff members who have helped me so much along the way: Lisa Dignadice, Korin Coombs, Sergio Mendoza, Jay Conlon, and Mark McLaughlin.

I thank my family for their support through this time, without which this thesis may not have been possible.

I thank all my new friends in the department who made studying physics at the graduate level such a joy.

I thank Vito Scarola for generously supplying us with the Monte Carlo code.

Finally, I would like to thank the Office of Research and Sponsored Programs at California State University, Long Beach and the Google Summer Research Assistantship for funding our research.

\singlespacing